On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2024-07-11 char-4k-bound/char-4k-bound.tex
[4k3] Various minor fixes

\author{
	N.N. Avdeev
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru},
	E.A. Lushina
	\footnote{TODO}
	\\
	\textit{Voronezh State University, Voronezh, Russia}
}

@@

\paragraph{Abstract.}
A point set $M$ in Euclidean plane is called an integral point set in semi-general position if all the distances between the
elements of $M$ are integers, and $M$ does not contain collinear triples.
We improve the linear lower bound for diameter of such sets in the particular case
when the characteristic of the set is of the form $4k+1$ or $4k+2$.
To achieve that, we combine hyperbolae-based and grid-based toolsets.

@@

	Using this toolset, in 2003 Solymosi proved~\cite{solymosi2003note} that
	$$
		\operatorname{diam} M \ge c \cdot \#M.
	$$
	Although Solymosi did not give the constant $c$ explicitly,
	it can be inferred from his proof that $c=\frac{1}{24}$ [TODO].

@@

	Meanwhile in 1988 Kemnitz introduced~\cite{kemnitz1988punktmengen}
	a characteristic of an IPS, that is a squarefree integer $q$ such as the area
	of any triangle formed by any triple of points from the IPS is comparable with $\sqrt{q}$.
	(Indeed, Kemnitz proved this fact for any point set with rational distances ---
	in contrast with IPS, those can be infinite even they contain non-collinear triples,
	see~\cite{huff1948diophantine} for an example of construction
	and~\cite{solymosi2010question} for some known limitations.)
	In 2000s, Kurz introduced~\cite{kurz2005characteristic} the function $d(2,n)$ that evaluates
	to the minimal possible diameter of planar IPS of cardinality $n$.
	Then Kurz employed Kemnitz's results and found~\cite[Subsection 4.2]{kurz2008minimum} exact values of $d(2,n)$
	up to $n=122$ by exhaustive computer search.
	(Taking the characteristic into consideration allows to boost such search significantly ---
	basically because all triples of an IPS form triangles with equal characteristics.)

@@

	In the present paper, we put the power of Erdös and Kemnitz approaches together. Due to squarefree nature of characteristic, it can be of the form $4k+1$, $4k+2$ or $4k+3$, where $k$ is integer.
	We prove that for a particular case of characteristic $4k+1$ and $4k+2$
	the bound~\eqref{eq:chebsb_lower_bound} can be improved to
	\begin{equation}
		\operatorname{diam} M \ge \left( \frac{25}{36} n \right)^{5/4}
		.
	\end{equation}

@@

\begin{definition}
	\label{def:IPS}
	A planar integral point set (IPS) is a set $M$
	of non-collinear points in the plane $\mathbb{R}^{2}$ such that
	for any pair of points $M_{1}, M_{2} \in \mathcal{P}$
	the Euclidean distance $|M_{1}M_{2}|$
	between points $M_{1}$ and $M_{2}$ is integral.
	Notation: $M\in\mathfrak{M}$, and also $M\in\mathfrak{M}_n$ for $n=\#M$.
\end{definition}

@@

\begin{definition}
	\label{def:IPS_semi_general}
	A planar IPS $M$ is said to be in \emph{semi-general position}
	if no three points of $M$ are collinear.
	Notation: $M\in\overline{\mathfrak{M}}$, and also $M\in\overline{\mathfrak{M}}_n$ for $n=\#M$.
\end{definition}

@@

\begin{definition}
	The diameter of an integral point set $M$ is defined by setting
	\begin{equation}
		\operatorname{diam M} = \underset{M_{1}, M_{2} \in
		M}{\max} |M_{1}M_{2}|
		.
	\end{equation}
\end{definition}

@@

\begin{definition}
	A number is called \emph{squarefree} if its only perfect square divisor is 1.
	The first squarefree numbers are: 1, 2, 3, 5, 6, 7, 10, 11, 13,...
\end{definition}

@@

\begin{definition}
	If points $M_1, M_2 \in M \in \mathcal{M}$,
	then the line segment $M_1 M_2$ is said to be an \emph{edge} of $M$.
\end{definition}

The following result is due to Kemnitz:

@@

For the sake of completeness, we provide the proof for the Grid Theorem below.

\begin{proof}
	Let $M_1, M_2 \in M \in \mathfrak M$ and $|M_1 M_2| = m$.
	Set $M_1=(-m/2, 0)$, $M_2=(m/2, 0)$.
	Then for any $M_i \in M$, $M_i = (x,y)$ one has
	$|M_i M_1| = k \in \mathbb N_0$, $|M_i M_2| = n \in \mathbb N_0$.
	The point $M_i$ belongs to the intersection of two circles,
	whose equations are
	\begin{gather}
		\left(-\frac{m}{2} - x\right)^2 + y ^2 = k^2,
	\\
		\left( \frac{m}{2} - x\right)^2 + y ^2 = n^2,
	\end{gather}
	where $a+b\geq m$.

@@

Obviously, the 0-th Erdos curve is the perpendicular bisector of $M_1 M_2$,
and all the other Erdos curves are branches of cofocal hyperbolae.

On Figure~\ref{fig:Erdos_curves_numbered}, the Erdos curves are shown for an edge of length 3.

\begin{figure}
\center{\includegraphics[width=0.6\linewidth]{Erdos_curves_numbered.png}}
\caption{Erdos curves}
\label{fig:Erdos_curves_numbered}
\end{figure}

@@

\begin{lemma}
	\cite[Lemma 4]{our-vmmsh-2018};
	\cite[Lemma 2.4]{my-pps-linear-bound-2019}
	\label{lem:square_container}
	Let $M\in\mathfrak{M}(2,n)$, $\operatorname{diam} M = d$.
	Then $M$ is situated in a square of side length $d$.
\end{lemma}

@@

As far as our attention will be mostly restricted to planar integral point sets
with characteristic of the form $4k+1$ and $4k+2$ in semi-general position.
If an IPS $M$ satisfies these conditions,
we will write that
$M\in\overline{\mathfrak{M}}'$, and also $M\in\overline{\mathfrak{M}}'_n$ for $n=\#M$

@@

\begin{figure}
\center{\includegraphics[width=0.6\linewidth]{char385.png}}
\caption{IPS of cardinality 16 and diameter 2189}
\label{fig:char385}
\end{figure}

In~\cite{kreisel2008heptagon}, the first ever known
planar integral point set $M_7 \in \dot{\mathfrak{M}}_7$ is given,
see Fig.~\ref{fig:heptagon2}.
Its coordinates are
\begin{multline}
\sqrt{2002}/2227 * \{ (0;0), (2227^2\cdot10;0), (26127018;932064), (32 142 553; 411 864),
\\
	 (17615968;238464), (7 344 908;411 864), (19079044; 54168)\}
	 ,
\end{multline}
and
$
	\chr M_7 = 2002 = 4\cdot 500 + 2
$.

@@

Also the largest known rails IPS presented in~\cite{}[TODO:Omsk!]
that has 104 points on one straight line and the rest 2 on another
(that is the cardinality of 106) has the characteristic of $154 = 4 \cdot 38 + 2$.
(We do not list the coordinates of that set here due to its diameter which is 2745754098774581800288844387372160.)

\begin{figure}
\center{\includegraphics[width=0.6\linewidth]{heptagon2.png}}
\caption{The heptagon in general position}
\label{fig:heptagon2}
\end{figure}

As for characteristic $4k+3$, we should mention that the \emph{upper} bound for the minimal diameter
of planar integral point set given in~\cite{harborth1993upper} employs IPS with characteristic $3$.
Moreover, all the IPS of minimal possible diameter provided in~\cite[\S 5, Fig. 1]{harborth1993upper}
(for cardinalities from 3 to 9) have characteristic of form $4k+3$.

For the sake of completeness, on Fig.~\ref{fig:11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}
we give an example of rails set
with 3 points on one line and 8 points on the other (first presented in~\cite{})
whose characteristic is
\begin{equation}
	255255 = 3 \cdot 5 \cdot 7 \cdot 11 \cdot 13 \cdot 17
	 = 4 \cdot 63813  + 3
\end{equation}
and whose coordinates are
\begin{multline}
\mathcal{P}_{3,8}=\sqrt{255255}/2*\{
	( 1767 ; -3);
	( 2791 ; -3);
	( 4071 ; -3);
\\
	( -306 ; 0);
	( 0 ; 0);
	( 1798 ; 0);
	( 2304 ; 0);
	( 2760 ; 0);
	( 3534 ; 0);
	( 4040 ; 0);
	( 4558 ; 0)
\}
\end{multline}

\begin{figure}
\center{\includegraphics[width=0.6\linewidth]{11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}}
\caption{The heptagon in general position}
\label{fig:11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}
\end{figure}

@@

\begin{lemma}
	\label{lem:pre_weeding_I}
	Any set $M = {A, B, C} \in \mathfrak{M}_3$ with edge $|AB| = m$, where $|AC| - |BC| = m - s$, $m, s \in \mathbb{N}$, and $s$ is an odd number and $s \leq m$, has a characteristic of the form $p = 4k + 3$, $k \in \mathbb{N}_0$.
\end{lemma}

\begin{proof}
	Let $|BC| = n$. Then, from the triangle inequality $|AC| < |AB| + |BC|$, we have that $|AC| = m + n - s$, $s \in \mathbb{N}$ and $s \leq m$. By the Grid Theorem, we introduce such coordinates that $A = (-\frac{m}{2}; 0)$, $B = (\frac{m}{2}; 0)$, and $C = (\frac{a}{2m}; \frac{b\sqrt{p}}{2m})$. We find the distance between points $A$ and $C$, and points $B$ and $C$ in coordinates, and form a system of equations
	\begin{equation}
		\left\{
		\begin{aligned}
		\frac{\sqrt{(a+m^2)^2+pb^2}}{2m}&=m+n-s.\\
		\frac{\sqrt{(a-m^2)^2+pb^2}}{2m}&=n
		\end{aligned}
		\right.
		\label{eq:29}
	\end{equation}
	Multiply each equation by $2m$ and square both sides of the equations in system (\ref{eq:29})
	\begin{equation}
	\left\{
	\begin{aligned}
	(a+m^2)^2+pb^2&=4m^2(m+n-s)^2,\\
	(a-m^2)^2+pb^2&=4m^2n^2
	\end{aligned}
	\right.
	\label{eq: 30}
	\end{equation}
	and then subtract the second equation from the first one:
	\begin{equation}
	(a+m^2)^2-(a-m^2)^2=4m^2(m+n-s)^2-4m^2n^2,
	\label{eq: 31}
	\end{equation}
	$$
	4m^2a=4m^2((m+n-s)^2-n^2),
	$$
	so
	\begin{equation}
	a=(m-s)(m+2n-s).
	\label{eq: 32}
	\end{equation}
	Substitute the obtained expression (\ref{eq:32}) into the second equation of the system (\ref{eq:30}).
	\begin{equation}
		((m-s)(m+2n-s)-m^2)^2+pb^2=4m^2n^2,
	\end{equation}
	that immediately gives
	\begin{equation}
		\label{eq:33}
		pb^2=s(2m+2n-s)(2n-s)(2m-s).
	\end{equation}
	According to the assumption, let $s=2t+1$, where $t\in\mathbb{N}_0$.
	Then equation (\ref{eq:33}) can be rewritten as:
	\begin{equation}
		pb^2=(2t+1)(2m+2n-2t-1)(2n-2t-1)(2m-2t-1).
		\label{eq:34.2}
	\end{equation}
	or
	\begin{eqnarray}
		pb^2+1 &=&4(-4t^4+8t^3m+8t^3n-8t^3-4t^2m^2-12t^2mn+12t^2m- {}\nonumber\\
			 &     &-4t^2n^2+12t^2n-6t^2+4tm^2n-4tmn^2-12tmn+6tm- {}\nonumber\\
			 &     &-4tn^2+6tn-2t+2m^2n-m^2+2mn^2-3mn+m-n^2+n).{}\nonumber\\
	\label{eq: 35}
	\end{eqnarray}
	For equation (\ref{eq:35}) to have integer solutions, it is necessary for $p$ and $b$ to be odd.
	The right-hand side is divisible by 4. Then $pb^2\equiv3\operatorname{mod}{4}$.
	But $b^{2}\equiv1(\operatorname{mod}4)$.
	Thus, $p=4k+3$, $k\in \mathbb{N}_{0}$.
\end{proof}

@@

\begin{theorem}[The Weeding Theorem I]
	\label{thm:weeding_I}
	Let $M = {M_1, M_2, M_3} \in \mathfrak{M}_3$ be an IPS of semi-general position with a characteristic different from $4k+3$, $k \in \mathbb{N}_0$. Then, the length of the edge $M_1 M_2$ and its $n$-th Erdős curve, which contains the point $M_3$, have the same parity.
\end{theorem}

\begin{proof}
	Let $|M_1 M_2| = m$, $m \in \mathbb{N}$, and let the $n$-th Erdős curve satisfy $|M_1 M_3| - |M_2 M_3| = n$.
	If $m$ is an odd number, then by Remark \ref{rm: 2}, the difference $n = |M_1 M_3| - |M_2 M_3| = m - s$, where $s$ is an even number, is also an odd number.
	Let $m$ be an even number; then $n = |M_1 M_3| - |M_2 M_3| = m - s$ is an even number, as the difference of two even numbers.
\end{proof}

@@

\begin{lemma}
	\ref{lem:pre_weeding_II}
	Every set $M = {A, B, C} \in \mathfrak{M}_3$ with an even edge $|AB| = 2q$, where $|AC| - |BC| = 2q - s$, $q, s \in \mathbb{N}$, $s$ is an odd number and $s \leq 2q$, has a characteristic of the form $p = 8k + 7$, $k \in \mathbb{N}_0$.
\end{lemma}

\begin{proof}
	Let us set $m = 2q$ in the Lemma~\ref{lem:pre_weeding_I}.
	Then equation \eqref{eq:33} turns into
	\begin{equation}
		\label{eq:33.1}
		pb^2 = s(4q + 2n - s)(2n - s)(4q - s).
	\end{equation}
	Taking into account that $s = 2t + 1$, $t \in \mathbb{N}_0$,
	we bring equation (\ref{eq:33.1}) to the form:
	\begin{equation}
	pb^2 = (2t + 1)(4q + 2n - 2t - 1)(2n - 2t - 1)(4q - 2t - 1).
	\label{eq: 34.2}
	\end{equation}
	or, after expansion,
	\begin{eqnarray}
		pb^2 + 1&=& 8(-2t^4+8t^3q+4t^3n-4t^3-8t^2q^2-12t^2qn+12t^2q- {}\nonumber\\
			 &     &-2t^2n^2+6t^2n-3t^2+8tq^2n-4tqn^2-12tqn+6tq- {}\nonumber\\
			 &     &-2tn^2+3tn-t+4q^2n-2q^2+2qn^2-3qn+q)-  {}\nonumber\\
			   &     &-4n(n-1).
		\label{eq: 35.1}
	\end{eqnarray}
	Among two consecutive natural numbers $n$ and $(n-1)$,
	exactly one of them is divisible by 2.
	Therefore, the expression $4n(n-1)\equiv0\pmod{8}$.
	Thus, the right-hand side of equation (\ref{eq:35.1}) is an even number and a multiple of 8.
	Then $pb^2\equiv7\pmod{8}$.
	A necessary condition for the existence of an integer solution to equation (\ref{eq:35.1})
	is that numbers $p$ and $b$ must be odd.
	But $b^2\equiv1\pmod{8}$, so $p=8k+7$, $k\in\mathbb{N}_0$.
\end{proof}

@@

\begin{proof}
	Indeed, consider the triangle $ABC$ and let $|BC|=a$, $|AC|=b$.
	From the triangle inequality $|AB| < |BC|+|AC|$,
	we can represent the length of side $AB$ as $|AB|=a+b-s$, $s \in \mathbb{N}$ and $s \leq a$.
	For $s=1$, the conditions of TODO are satisfied: $s$ is an odd number and $s \leq a$.
	Therefore, the triangle with sides $a$, $b$, and $c=a+b-1$
	has a characteristic of the form $p=4k+3$, $k\in \mathbb{N}_0$.
\end{proof}

@@

\section{Conclusion}
	The bound proved above (as well as the one (TODO)) may appear to be far from precise values of $\overline{d}(2,n)$.
	However, it's easy to see that values of $d(2;n)$ tend to repeat often;
	thus, it is rather not unrealistic that the bounds may converge to the precise values.

>>>>

\author{
	N.N. Avdeev
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru},
	E.A. Lushina
	%\footnote{TODO}
	\\
	\textit{Voronezh State University, Voronezh, Russia}
}

@@

\paragraph{Abstract.}
A point set $M$ in Euclidean plane is called an integral point set in semi-general position if all the distances between the
elements of $M$ are integers, and $M$ does not contain collinear triples.
We improve the lower bound for diameter of such sets in the particular case
when the characteristic of the set is of the form $4k+1$ or $4k+2$.
To achieve that, we combine hyperbolae-based and grid-based toolsets.

@@

	Using this toolset, in 2003 Solymosi proved~\cite{solymosi2003note} that
	$$
		\operatorname{diam} M \ge c \cdot \#M.
	$$
	Although Solymosi did not give the constant $c$ explicitly,
	it can be inferred~\cite{our-vmmsh-2018-translit} from his proof that $c=\frac{1}{24}$.

@@

	Meanwhile in 1988 Kemnitz introduced~\cite{kemnitz1988punktmengen}
	a characteristic of an IPS, that is a squarefree integer $q$ such as the area
	of a triangle formed by any triple of points from the IPS is comparable with $\sqrt{q}$.
	(Indeed, Kemnitz proved this fact for any point set with rational distances ---
	in contrast with IPS, those can be infinite even if they contain non-collinear triples,
	see~\cite{huff1948diophantine} for an example construction
	and~\cite{solymosi2010question} for some known limitations.)
	In 2000s, Kurz introduced~\cite{kurz2005characteristic} the function $d(2,n)$ that evaluates
	to the minimal possible diameter of planar IPS of cardinality $n$.
	Then Kurz employed Kemnitz's results and found~\cite[Subsection 4.2]{kurz2008minimum} exact values of $d(2,n)$
	up to $n=122$ by exhaustive computer search.
	(Taking the characteristic into consideration allows to boost such search significantly ---
	basically because all triples of an IPS form triangles with equal characteristic.)

@@

	In the present paper, we put the power of Erdös's and Kemnitz's approaches together. Due to squarefree nature of characteristic, it can be of the form $4k+1$, $4k+2$ or $4k+3$, where $k$ is integer.
	We prove that for a particular case of characteristic $4k+1$ and $4k+2$
	the bound~\eqref{eq:chebsb_lower_bound} can be improved to
	\begin{equation}
		\operatorname{diam} M \ge \left( \frac{25}{36} n \right)^{5/4}
		.
	\end{equation}

@@

\begin{definition}
	\label{def:IPS}
	A planar integral point set (IPS) is a set $M$
	of non-collinear points in the plane $\mathbb{R}^{2}$ such that
	for any pair of points $M_{1}, M_{2} \in M$
	the Euclidean distance $|M_{1}M_{2}|$
	between points $M_{1}$ and $M_{2}$ is integral.
	Notation: $M\in\mathfrak{M}$, and also $M\in\mathfrak{M}_n$ for $n=\#M$.
\end{definition}

@@

\begin{definition}
	\label{def:IPS_semi_general}
	A planar IPS $M$ is said to be in \emph{semi-general position}
	if no three points of $M$ are collinear.
	Notation: $M\in\dot{\mathfrak{M}}$, and also $M\in\dot{\mathfrak{M}}_n$ for $n=\#M$.
\end{definition}

@@

\begin{definition}
	The diameter of an integral point set $M$ is defined by setting
	\begin{equation}
		\operatorname{diam} M = \underset{M_{1}, M_{2} \in
		M}{\max} |M_{1}M_{2}|
		.
	\end{equation}
\end{definition}

@@

\begin{definition}
	A number is called \emph{squarefree} if its only perfect square divisor is 1.
	The first squarefree numbers are: 1, 2, 3, 5, 6, 7, 10, 11, 13, ...
\end{definition}

@@

\begin{definition}
	If points $M_1, M_2 \in M \in \mathfrak{M}$,
	then the line segment $M_1 M_2$ is said to be an \emph{edge} of $M$.
\end{definition}

The following result is due to Kemnitz~\cite{kemnitz1988punktmengen}:

@@

For the sake of completeness, we sketch the proof for the Grid Theorem below.

\begin{proof}
	Let $M_1, M_2 \in M \in \mathfrak M$ and $|M_1 M_2| = m$.
	Set $M_1=(-m/2, 0)$, $M_2=(m/2, 0)$.
	Then for any $M_i \in M$, $M_i = (x,y)$ one has
	$|M_i M_1| = k \in \mathbb N_0$, $|M_i M_2| = n \in \mathbb N_0$.
	The point $M_i$ belongs to the intersection of two circles,
	whose equations are
	\begin{gather}
		\left(-\frac{m}{2} - x\right)^2 + y ^2 = k^2,
	\\
		\left( \frac{m}{2} - x\right)^2 + y ^2 = n^2,
	\end{gather}
	where $k+n\geq m$.

@@

Obviously, the 0-th Erdos curve is the perpendicular bisector of $M_1 M_2$,
and all the other Erdos curves are branches of cofocal hyperbolae.
On Figure~\ref{fig:Erdos_curves_numbered}, the Erdos curves are shown for an edge of length 3.

\begin{figure}
\center{\includegraphics[width=0.95\linewidth]{Erdos_curves_numbered.png}}
\caption{Erdos curves}
\label{fig:Erdos_curves_numbered}
\end{figure}

@@

\begin{lemma}
	\cite[Lemma 4]{our-vmmsh-2018-translit};
	\cite[Lemma 2.4]{my-pps-linear-bound-2019}
	\label{lem:square_container}
	Let $M\in\mathfrak{M}(2,n)$, $\operatorname{diam} M = d$.
	Then $M$ is situated in a square of side length $d$.
\end{lemma}

@@

Our attention will be mostly restricted to planar integral point sets
with characteristic of the form $4k+1$ and $4k+2$ in semi-general position.
Thus, if an IPS $M$ satisfies these conditions,
we will write that
$M\in\overline{\mathfrak{M}}'$, and also $M\in\overline{\mathfrak{M}}'_n$ for $n=\#M$.

@@

\begin{figure}
\center{\includegraphics[width=0.95\linewidth]{char385.png}}
\caption{IPS of cardinality 16 and diameter 2189}
\label{fig:char385}
\end{figure}

In~\cite{kreisel2008heptagon}, the first ever known
planar integral point set $M_7 \in \dot{\mathfrak{M}}_7$ is given,
see Figure~\ref{fig:heptagon2}.
Its coordinates are
\begin{multline}
\sqrt{2002}/2227 * \{ (0;0), (2227^2\cdot10;0), (26127018;932064), (32 142 553; 411 864),
\\
	 (17615968;238464), (7 344 908;411 864), (19079044; 54168)\}
	 ,
\end{multline}
and
$
	\chr M_7 = 2002 = 4\cdot 500 + 2
$.

@@

Also the largest known rails IPS presented in~\cite{momot2022example}
with 104 points on one straight line and the rest 2 on another
(that gives the cardinality of 106) has the characteristic of $154 = 4 \cdot 38 + 2$.
(We do not list the coordinates of that set here due to its diameter which is 2745754098774581800288844387372160.)

\begin{figure}
\center{\includegraphics[width=0.95\linewidth]{heptagon2.png}}
\caption{The heptagon in general position}
\label{fig:heptagon2}
\end{figure}

As for characteristic $4k+3$, we should mention that the \emph{upper} bound for the minimal diameter
of planar integral point set given in~\cite{harborth1993upper} employs IPS with characteristic $3$.
Moreover, all the IPS of minimal possible diameter provided in~\cite[\S 5, Figure 1]{harborth1993upper}
(for cardinalities from 3 to 9) have characteristic of form $4k+3$.

For the sake of completeness, on Figure~\ref{fig:11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}
we give an example of rails set
with 3 points on one line and 8 points on the other (first presented in~\cite[Figure 1]{avdeev2019particular})
whose characteristic is
\begin{equation}
	255255 = 3 \cdot 5 \cdot 7 \cdot 11 \cdot 13 \cdot 17
	 = 4 \cdot 63813  + 3
\end{equation}
and whose coordinates are
\begin{multline}
\mathcal{P}_{3,8}=\sqrt{255255}/2*\{
	( 1767 ; -3);
	( 2791 ; -3);
	( 4071 ; -3);
\\
	( -306 ; 0);
	( 0 ; 0);
	( 1798 ; 0);
	( 2304 ; 0);
	( 2760 ; 0);
	( 3534 ; 0);
	( 4040 ; 0);
	( 4558 ; 0)
\}
\end{multline}

\begin{figure}
\center{\includegraphics[width=0.95\linewidth]{11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}}
\caption{The rails set with characteristic 255255}
\label{fig:11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}
\end{figure}

@@

\begin{lemma}
	\label{lem:pre_weeding_I}
	Any set $M = \{A, B, C\} \in \mathfrak{M}_3$ with edge $|AB| = m$, where $|AC| - |BC| = m - s$, $m, s \in \mathbb{N}$, and $s$ is an odd number and $s \leq m$, has a characteristic of the form $p = 4k + 3$, $k \in \mathbb{N}_0$.
\end{lemma}

\begin{proof}
	Let $|BC| = n$. Then, from the triangle inequality $|AC| < |AB| + |BC|$, we have that $|AC| = m + n - s$, $s \in \mathbb{N}$ and $s \leq m$. By the Grid Theorem, we introduce such coordinates that $A = (-\frac{m}{2}; 0)$, $B = (\frac{m}{2}; 0)$, and $C = (\frac{a}{2m}; \frac{b\sqrt{p}}{2m})$. We find the distance between points $A$ and $C$, and points $B$ and $C$ in coordinates, and form a system of equations
	\begin{equation}
		\label{eq:29}
		\begin{cases}
		\frac{\sqrt{(a+m^2)^2+pb^2}}{2m}&=m+n-s.\\
		\frac{\sqrt{(a-m^2)^2+pb^2}}{2m}&=n
		\end{cases}
	\end{equation}
	Multiply each equation by $2m$ and square both sides of the equations in system (\ref{eq:29})
	\begin{equation}
		\label{eq:30_pre_weeding_I}
		\begin{cases}
		(a+m^2)^2+pb^2&=4m^2(m+n-s)^2,\\
		(a-m^2)^2+pb^2&=4m^2n^2
		\end{cases}
	\end{equation}
	and then subtract the second equation from the first one:
	\begin{equation}
	(a+m^2)^2-(a-m^2)^2=4m^2(m+n-s)^2-4m^2n^2,
	\label{eq: 31}
	\end{equation}
	$$
	4m^2a=4m^2((m+n-s)^2-n^2),
	$$
	so
	\begin{equation}
		\label{eq:32_pre_weeding_I}
		a=(m-s)(m+2n-s).
	\end{equation}
	Substitute the obtained expression~\eqref{eq:32_pre_weeding_I}
	into the second equation of the system~\eqref{eq:30_pre_weeding_I}:
	\begin{equation}
		((m-s)(m+2n-s)-m^2)^2+pb^2=4m^2n^2,
	\end{equation}
	that immediately gives
	\begin{equation}
		\label{eq:33}
		pb^2=s(2m+2n-s)(2n-s)(2m-s).
	\end{equation}
	According to the assumption, let $s=2t+1$, where $t\in\mathbb{N}_0$.
	Then equation (\ref{eq:33}) can be rewritten as:
	\begin{equation}
		\label{eq:34.2}
		pb^2=(2t+1)(2m+2n-2t-1)(2n-2t-1)(2m-2t-1)
	\end{equation}
	or
	\begin{eqnarray}
		pb^2+1 &=&4(-4t^4+8t^3m+8t^3n-8t^3-4t^2m^2-12t^2mn+12t^2m- {}\nonumber\\
			 &     &-4t^2n^2+12t^2n-6t^2+4tm^2n-4tmn^2-12tmn+6tm- {}\nonumber\\
			 &     &-4tn^2+6tn-2t+2m^2n-m^2+2mn^2-3mn+m-n^2+n).%{}\nonumber\\
	\label{eq:35}
	\end{eqnarray}
	If equation (\ref{eq:35}) has integer solutions, then both $p$ and $b$ are odd.
	The right-hand side is divisible by 4. Then $pb^2\equiv3\operatorname{mod}{4}$.
	But $b^{2}\equiv1(\operatorname{mod}4)$.
	Thus, $p=4k+3$, $k\in \mathbb{N}_{0}$.
\end{proof}

@@

\begin{theorem}[The Weeding Theorem I]
	\label{thm:weeding_I}
	Let $M = \{M_1, M_2, M_3\} \in \mathfrak{M}_3$ be an IPS of semi-general position with a characteristic different from $4k+3$, $k \in \mathbb{N}_0$. Then, the length of the edge $M_1 M_2$ and its $n$-th Erdős curve, which contains the point $M_3$, have the same parity.
\end{theorem}

\begin{proof}
	Let $|M_1 M_2| = m$, $m \in \mathbb{N}$, and let the $n$-th Erdős curve satisfy $|M_1 M_3| - |M_2 M_3| = n$.
	If $m$ is an odd number, then by Lemma~\ref{lem:pre_weeding_I}, the difference $n = |M_1 M_3| - |M_2 M_3| = m - s$, where $s$ is an even number, is also an odd number.
	Let $m$ be an even number; then $n = |M_1 M_3| - |M_2 M_3| = m - s$ is an even number, as the difference of two even numbers.
\end{proof}

@@

\begin{lemma}
	\label{lem:pre_weeding_II}
	Every set $M = \{A, B, C\} \in \mathfrak{M}_3$ with an even edge $|AB| = 2q$, where $|AC| - |BC| = 2q - s$, $q, s \in \mathbb{N}$, $s$ is an odd number and $s \leq 2q$, has a characteristic of the form $p = 8k + 7$, $k \in \mathbb{N}_0$.
\end{lemma}

\begin{proof}
	Let us set $m = 2q$ in the Lemma~\ref{lem:pre_weeding_I}.
	Then equation \eqref{eq:33} turns into
	\begin{equation}
		\label{eq:33.1}
		pb^2 = s(4q + 2n - s)(2n - s)(4q - s).
	\end{equation}
	Taking into account that $s = 2t + 1$, $t \in \mathbb{N}_0$,
	we bring equation (\ref{eq:33.1}) to the form:
	\begin{equation}
	pb^2 = (2t + 1)(4q + 2n - 2t - 1)(2n - 2t - 1)(4q - 2t - 1).
	\label{eq: 34.2}
	\end{equation}
	or, after expansion,
	\begin{eqnarray}
		pb^2 + 1&=& 8(-2t^4+8t^3q+4t^3n-4t^3-8t^2q^2-12t^2qn+12t^2q- {}\nonumber\\
			 &     &-2t^2n^2+6t^2n-3t^2+8tq^2n-4tqn^2-12tqn+6tq- {}\nonumber\\
			 &     &-2tn^2+3tn-t+4q^2n-2q^2+2qn^2-3qn+q)-  {}\nonumber\\
			   &     &-4n(n-1).
		\label{eq:35.1}
	\end{eqnarray}
	Among two consecutive natural numbers $n$ and $(n-1)$,
	exactly one of them is divisible by 2.
	Therefore, the expression $4n(n-1)\equiv0\pmod{8}$.
	Thus, the right-hand side of equation (\ref{eq:35.1}) is an even number and a multiple of 8.
	Then $pb^2\equiv7\pmod{8}$.
	A necessary condition for the existence of an integer solution to equation (\ref{eq:35.1})
	is that numbers $p$ and $b$ must be odd.
	But $b^2\equiv1\pmod{8}$, so $p=8k+7$, $k\in\mathbb{N}_0$.
\end{proof}

@@

\begin{proof}
	Indeed, consider the triangle $ABC$ and let $|BC|=a$, $|AC|=b$.
	From the triangle inequality $|AB| < |BC|+|AC|$,
	we can represent the length of side $AB$ as $|AB|=a+b-s$, $s \in \mathbb{N}$ and $s \leq a$.
	For $s=1$, the conditions of Lemma~\ref{lem:pre_weeding_I} are satisfied: $s$ is an odd number and $s \leq a$.
	Therefore, the triangle with sides $a$, $b$, and $c=a+b-1$
	has a characteristic of the form $p=4k+3$, $k\in \mathbb{N}_0$.
\end{proof}

@@

\section{Conclusion}
	The bound proved above (as well as~\eqref{eq:chebsb_lower_bound}) may appear to be far from precise values of $\overline{d}(2,n)$.
	However, it's easy to see that values of $d(2;n)$ tend to repeat often;
	thus, it is rather not unrealistic that the bounds may converge to the precise values.
